Data Management for LSST Special Programs

### 2024-04-09 sec_proc.tex
Update sec_proc.tex
Co-authored-by: Eric Bellm <ecbellm@uw.edu>

Consider a Special Program in which a special region of sky is observed with standard
visits but a pecial strategy or cadence which is significantly distinct from the Main Survey
observing modes, and lasts for a limited amount of time.
For example, a short-term survey of the Magellanic Clouds, with dual primary science
goals in time-domain and static-sky science.

>>>>

Consider a Special Program in which a special region of sky is observed with standard
visits but a special strategy or cadence which is significantly distinct from the Main Survey
observing modes, and lasts for a limited amount of time.
For example, a short-term survey of the Magellanic Clouds, with dual primary science
goals in time-domain and static-sky science.
